INTELLIGENT SYSTEMS

### 2021-04-12 slides/slides_paper6.tex
start foreground
finish slide paper6

>>>>

\begin{frame}{EXPERIMENTS - Semantic Segmentation Results}
    The \emph{Intersection over Union} (IoU), averaged over 21, categories is used as an 
    evaluation index of the semantic segmentation and foreground segmentation. 
    \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=0.7\textwidth}
                \begin{tabular}{|c|c|}
                    \hline
                    Training Mask Type & IoU(\%)\\
                    \hline
                    Coarse Masks & 32.5 \\
                    Bounding Boxes & 35.2 \\
                    Enhanced Masks & 47.7 \\
                    Refined Masks & 50.4 \\
                    \hline
                \end{tabular}
                \end{adjustbox}
                \caption{The performance of semantic segmentation networks evalueted in the validation split of PASCAL VOC dataset in the mean IoU (higher is better).}
            \end{table}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{figure}[h!]
                \centering
                \includegraphics[width = 1 \linewidth]{images/paper6/GrabCut.png}
                \centering
                \caption{Enhancement with GrubCut application}
            \end{figure}
        \end{minipage}
    \end{minipage}
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=0.7\textwidth}
        \begin{tabular}{|c|c|c|}
            \hline
            Methods & mIoU(val) & mIoU(test)\\
            \hline
            Supervision: Object-level Labels & &\\
            SDI \cite{0876055513} & 65.7 & 67.5\\
            \hline
            Supervision: Image-level Labels & &\\
            Bootstrap \cite{0876055555} & 63.0 & 63.9\\
            \bfseries{The proposed weakly supervised method} & \bfseries{61.9} & \bfseries{62.8}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Comparison, in terms of IoU score, between different models.}
        \label{IoU score comparison}
    \end{table}
\end{frame}

\begin{frame}{EXPERIMENTS - Foreground Segmentation Results}
    With an architecture similar to \emph{FPN} \footfullcite{0876055543}, the new network is called the \emph{Dilated Feature Pyramid 
    Network} (DFPN). This network has several dilated layers, in three branches, 
    added to enlarge the receptive field of the network. The features generated 
    by these layers are aggregated to make a prediction. From the performance obtained, the proposed 
    model, which is remembered to be weakly supervised, manages to achieve the 
    performance of the supervised models, with a difference of 2.06\% compared 
    to the supervised \emph{PixelObjectness}.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c||c|c|c|c||c|c|c|c|}
            \hline
            \multirow{2}{*}{\bfseries{Methods}} & \multicolumn{4}{c||}{\bfseries{MIT dataset (subset)}} & \multicolumn{4}{c|}{\bfseries{MIT dataset (full)}} \\            & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} & \bfseries{Ariplane} & \bfseries{Car} & \bfseries{Horse}  & \bfseries{Average} \\
            \hline
            \bfseries{\#Images} & 82 & 89 & 93 & N/A & 470 & 1208 & 810 & N/A\\
            \hline
            UnsupervisedSeg \cite{0876055520} & 61.37 & 70.52 & 55.09 &62.32 & N/A & N/A & N/A & N/A\\
            \hline
            PixelObjectness \cite{0876055538} & 66.43 & 85.07 & 60.85 &70.78 & 66.18 & 84.80 & 64.90 & 71.96\\
            \hline 
            \bfseries{FPN-Baseline} & 61.09 & 76.22 & 57.89 & \bfseries{65.08} & 61.93 & 75.94 & 64.03 & \bfseries{67.3}\\
            \hline
            \bfseries{Proposed Method} & 64.92 & 77.60 & 60.36 & \bfseries{67.63(+2.57)} & 65.88 & 77.07 & 65.82 & \bfseries{69.59(+2.29)}\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Quantitative Results of Foreground Segmentation on MIT object Discovery Dataset.}
    \end{table}
\end{frame}

\begin{frame}{CONCLUSION}
    The proposed framework, based on a weakly supervide model, is able to 
    achieve the performance of the full supervised models that obtain better 
    results at the state of the art. it is also capable of recognizing multiple categories of objects in an image (Fig. \ref{fig:segmentationCategories}). Despite the efforts made to arrive at such 
    results, there are several classes in which the model fails to generate 
    good masks (Fig. \ref{fig:classes}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 0.6 \linewidth]{images/paper6/multiple segmentation.png}
        \centering
        \caption{Example of semantic segmentation on different categories.}
        \label{fig:segmentationCategories}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = 1 \linewidth]{images/paper6/classes.png}
        \centering
        \caption{Score of IoU in some classes.}
        \label{fig:classes}
    \end{figure}
\end{frame}
